% ====   Preliminaries   ====
\section{Automorphisms}
In addition to in Robinson, this section's material is commonly found in group theory textbooks, including Chapter 6 of
Burnside's \textit{Theory of Groups}\footcite[Ch. 6]{burnside1911} and Chapter 4 of Ledermann's \textit{Introduction to
the Theory of Finite Groups}\footcite[Ch. 4]{ledermann1961}.

\begin{definition}
    \raggedright
    If \(G\) and \(H\) are groups with elements \(g_1,\, g_2 \in G\), then a map:
    \[\phi:G \to H\]
    is a \emph{homomorphism} if:
    \[(g_1 g_2)\phi = (g_1\phi)(g_2\phi)\]
    If \(\phi\) is bijective, then we call it an \emph{isomorphism}, with \(G \cong H\) denoting that \(G\) is
    isomorphic to \(H\).
    And if \(\phi\) is an isomorphism from \(G\) to itself, then we call it an \emph{automorphism} of
    \(G\).
\end{definition}

\begin{lemma}
    \raggedright
    The set of all automorphisms of a group \(G\) form a group under composition.
    Indeed, this is called the \emph{automorphism group} of \(G\), denoted \(\Aut{G}\).
\end{lemma}

\begin{proof}
    Let \(A = \Aut{G} = \{\,\phi:G \to G \mid \phi\ \text{is an isomorphism}\,\}\), and let \(\phi \in A\).
    Denote an element of \(G\) by \(g\).

    We know already that the composition of two isomorphisms is an isomorphism, so \(A\) is closed under composition.

    The identity map, \(\iota:g \mapsto g\), is certainly an automorphism of \(G\) and so \(A\) is non-empty.

    Indeed, \(\iota:g \mapsto g\) is the identity of \(A\), since:
    \[g\phi\iota = (g\phi)\iota = g\phi \quad \text{and} \quad g\iota\phi = (g\iota)\phi = g\phi\]
    And inverses clearly exist, because automorphisms are bijections, and bijections are invertible.
    Hence \(A = \Aut{G}\) is a group.
\end{proof}

\begin{lemma}\label{lem:aut}
    \raggedright
    The automorphism group of \(C_n\) is isomorphic to the multiplicative group
    of integers mod \(n\).

    i.e. \(\Aut{C_n} \cong \units{n}\)
\end{lemma}

\begin{proof}
    Let \(C_n = \langle x \rangle\).
    Any automorphism, \(\phi\) of \(C_n\) has the property:
    \[(x^i)\phi = {(x\phi)}^i\]
    Hence \(\phi\) is determined by its effect on a generator, \(x\), and preserves element
    order.
    In particular, \(\phi\) sends generators to generators.
    So for \(\phi\) to be an automorphism, it must send \(x\) to another generator, say \(x^k\).
    An element \(x^k\) generates \(C_n\) if \(x^k\) has order \(n\), i.e.\ when \(k\) and \(n\) are co-prime.
    Denote the automorphism sending \(x\) to \(x^k\) by \(\phi_k\).

    Let's now investigate how these automorphisms behave.
    Let \(\phi_k, \phi_l \in \Aut{C_n}\), and consider:
    \[x\phi_k\phi_l = (x^k)\phi_l = {(x^k)}^l = x^{(kl)} = x\phi_{kl} \pmod{n}\]
    Because multiplication modulo \(n\) is commutative, \(x^{kl} = x^{lk}\), so \(\Aut{C_n}\) is abelian.

    Now consider \(\theta:\Aut{C_n} \to \units{n}\) defined by \(\phi_k\theta = k\).
    We will show \(\theta\) is an isomorphism.
    Every \(k \in \units{n}\) is co-prime to \(n\) and so \(x^k\) is a generator of \(C_n\), hence there is some \(\phi_k
    \in \Aut{C_n}\) such that \(\phi_k\theta = k\).
    So \(\theta\) is surjective.
    If \(\phi_k\theta = \phi_l\theta\) then \(k = l\), so \(\theta\) is also injective.
    Finally, \(\theta\) is a homomorphism because:
    \[(\phi_k\phi_l)\theta = \phi_{kl}\theta = kl = (\phi_k\theta)(\phi_l\theta)\]
    So \(\theta:\Aut{C_n} \to \units{n}\) is an isomorphism.
\end{proof}

\begin{definition}
    \raggedright
    A subgroup \(H\) of a group \(G\) is called \emph{characteristic} if it is fixed by all automorphisms of
    \(G\).

    i.e.\ for an automorphism \(\phi\) of \(G\), \(H\phi = H\).
\end{definition}

\begin{lemma}\label{lem:char}
    \raggedright
    Let \(G\) be a group with normal subgroup \(H\), and let \(K\) be characteristic in \(H\).
    Then \(K\) is a normal subgroup of \(G\).
\end{lemma}

\begin{proof}
    Consider the map \(\phi_g:G \to G\) defined by \(\phi_g:x \mapsto g^{-1}xg\) for elements \(x,\,g \in G\).
    We will show that this is an automorphism of \(G\).
    For \(x,\,y \in G\):
    \[x\phi_g y\phi_g = (g^{-1}xg)(g^{-1}yg) = g^{-1}(xy)g = (xy)\phi_g\]
    Hence \(\phi_g\) is a homomorphism.
    Moreover, we can check that \(\phi_g\) is invertible with inverse \(\phi_{g^{-1}}\).
    So \(\phi_g\) is indeed an automorphism of G.

    Because \(H\) is normal, \(H\phi_g = H\).
    So \(\phi_g\) is an automorphism of \(H\) too.
    And so \(\phi_g\) maps \(K\) to itself, because it is characteristic.
    Hence:
    \[\{\,g^{-1}kg \mid k \in K\,\} = K\]
    So \(K\) is normal in \(G\).
\end{proof}

% ====   Semidirect Product   ====
\section{Semidirect Product}
A way to combine, or describe combinations of groups will be among the most used tools in this report!
The learning from this section is mostly from \textit{MT5864, Advanced Group Theory}, and can be found in
Robinson.\footcite{robinson1982}
The direct product is used commonly throughout group theory:
\begin{definition}
    \raggedright
    For groups \(N\) and \(H\), the \emph{direct product}, \(G = N\times H\) is a group of ordered pairs of elements
    \((n, h)\) where \(n \in N\) and \(h \in H\) with the operation:
    \[(n_1, h_1)(n_2, h_2) = (n_1n_2, h_1h_2)\]
\end{definition}

Furthermore, we recall its properties:
\begin{lemma}
    If \(\bar{N} = N \times \bm{1}\) and \(\bar{H} = \bm{1} \times H\), then:
    \begin{enumerate}[(i)]
        \item \(\bar{N} \nrmsgp G\) and \(\bar{H} \nrmsgp G\)
        \item \(\bar{N} \cap \bar{H} = \bm{1}\)
        \item \(\bar{N}\bar{H} = \{\,nh \mid n \in N,\ h \in H\,\} = G\)
    \end{enumerate}
\end{lemma}

Now let's seek a slightly more general way to combine groups, by relaxing that \(H\) must be normal.
So if we have a group \(G\) with the following:
\[N \nrmsgp G,\ H \leqslant G,\ NH = G, \quad \text{and} \quad N \cap H = \bm{1}\]
consider the \emph{set}, (not the direct product):
\[N \times H = \{\,(n,\,h) \mid n \in N,\ h \in H\,\}\]
We want to give this set a group structure, such that it is isomorphic to \(G\).
In other words, we want to construct an isomorphism:
\[\phi:N \times H \to G \quad \text{defined by} \quad (n,\, h) \mapsto nh\]
and in doing so, find a suitable group structure for \(N {\times} H\).

To show \(\phi\) is injective, take \(n_1,\, n_2 \in N\) and \(h_1,\, h_2 \in H\), and assume \(n_1 h_1 = n_2 h_2\).
Then multiplying on the left by \(n_2^{-1}\) and on the right by \(h_1^{-1}\) gives:
\[n_2^{-1} n_1 = h_2 h_1^{-1}\]
On the left we have an element of \(N\) and on the right, an element of \(H\), so:
\[n_2^{-1} n_1 = h_2 h_1^{-1} \in N \cap H\]
But \(N \cap H = \bm{1}\) so then \(n_2^{-1} n_1 = h_2 h_1^{-1} = 1\).
Hence:
\[n_1 = n_2 \quad \text{and} \quad h_1 = h_2\]
To show \(\phi\) is surjective, consider the image, \(\im{\phi} = \{\,nh \mid n \in N,\ h \in H\,\}\).
This is by definition \(NH = G\), so \(\phi\) is surjective, and hence a bijection.

For \(\phi\) to be a homomorphism, we need:
\begin{equation*}
\begin{aligned}
    \relax[(n_1,\,h_1)(n_2,\,h_2)]\phi &= (n_1,\,h_1)\phi\,(n_2,\,h_2)\phi \\
    &= n_1 h_1 n_2 h_2 \\
    &= n_1 h_1 n_2 (h_1^{-1} h_1) h_2 \\
    &= (n_1 h_1 n_2 h_1^{-1})(h_1 h_2)
\end{aligned}
\end{equation*}
But \(N\) is normal in \(G\) so \(h_1 n_2 h_1^{-1}\) is just another element in \(N\), say \(n_3\).
So:
\[\relax[(n_1,\,h_1)(n_2,\,h_2)]\phi = (n_1 n_3)(h_1 h_2) = (n_1 n_3,\,h_1 h_2)\phi\]
We know that \(\phi\) is injective, so then:
\[(n_1,\,h_1)(n_2,\,h_2) = (n_1 n_3,\,h_1 h_2) \tag{\(\dagger\)}\]
This tells us the multiplication that will make \(NH\) a group.
Because \(N \nrmsgp G\), the map
\[n_2 \mapsto h_1 n_2 h_1^{-1} = n_3\]
is an automorphism of \(N\).

This gives rise to the formal definition:

\begin{definition}[Semidirect Product]
\raggedright
\mbox{}
\begin{enumerate}[(i)]
    \item

        For a group \(G\) with normal subgroup \(N\) and subgroup \(H\) with \(NH = G\) and \(N \cap H = \bm{1}\),
        \(G\) is the \emph{internal semidirect product} of \(N\) by \(H\), written \(G = N \rtimes H\).
    \item

        For groups \(N\) and \(H\), and a homomorphism \(\psi:H \to \Aut{N}\), the \emph{external semidirect product} of
        \(N\) by \(H\) via \(\psi\) is the set:
        \[N \times H = \{\,(n,\,h) \mid n \in N,\ h \in H\,\}\]
        with multiplication:
        \[(n_1,\,h_1)(n_2,\,h_2) = (n_1(n_2^{h_1\psi}),\,h_1 h_2)\]
        denoted:
        \[N \rtimes_{\psi} H\]
        We use the notation \(n_2^{h_1\psi}\) to mean the image of \(n_2\) under the automorphism \(h_1\psi\), both
        because it indicates conjugation, and is clearer.
\end{enumerate}
\end{definition}

We can verify that \(N {\times} H\) with this multiplication is indeed a group.
We have already seen that \(N {\times} H\) is closed under (\(\dagger\)).
The identity element is \((1,\ 1)\):
\[ (n,\, h)(1,\, 1) =  (n 1^{h\psi},\, h 1) = (n,\, h)\]
\[ (1,\, 1)(n,\, h) =  (1 n^{1\psi},\, 1 h) = (n,\, h)\]
And finally, inverses exist, with \({(n,\, h)}^{-1} = \left({(n^{-1})}^{{(h\psi)}^{-1}},\, h^{-1}\right)\):
\begin{align*}
    (n,\, h)\left({(n^{-1})}^{{(h\psi)}^{-1}},\, h^{-1}\right)
    &= \left(n {\left({(n^{-1})}^{{(h\psi)}^{-1}}\right)}^{h\psi},\, hh^{-1} \right) \\
    &= (n n^{-1},\, h h^{-1}) \\
    &= (1,\, 1)
\end{align*}
\begin{align*}
    \left({(n^{-1})}^{{(h\psi)}^{-1}},\, h^{-1}\right)(n,\, h)
    &= \left({(n^{-1})}^{{(h\psi)}^{-1}} n^{(h^{-1})\psi},\, h^{-1} h \right) \\
    &= \left({(n^{-1})}^{{(h\psi)}^{-1}} n^{{(h\psi)}^{-1}},\, h^{-1} h \right) \\
    &= \left({(n^{-1} n)}^{{(h\psi)}^{-1}},\, h^{-1} h \right)  \\
    &= \left(1^{{(h\psi)}^{-1}},\, 1 \right) \\
    &= (1,\, 1)
\end{align*}

So we have a group.

\begin{lemma}\label{lem:setprodorder}
    \raggedright
    For a group \(G\) with \(N \leqslant G\) and \(H \leqslant G\), with \(N \cap H = \bm{1}\) then:
    \[|NH| = |\{nh \mid n \in N, h \in H\}| = |N| \cdot |H|\]
\end{lemma}

\begin{proof}
    We just saw above that if \(N \nrmsgp G\), for elements \(n \in N\) and \(h \in H\), the map:
    \[\phi:N \times H \to NH \quad \text{defined by} \quad (n,\,h) \mapsto nh\]
    is a bijection.
    We only used the normality of \(N\) for the homomorphism property of \(\phi\), which we don't need here, hence
    \(\phi\) is still a bijection if \(N \leqslant G\).
    The result follows immediately from this.
\end{proof}

\begin{lemma}\label{lem:semiisom}
    \raggedright
    Let \(N\) and \(H\) be groups, and \(\alpha \in \Aut{H}\).
    Then the semidirect products via the homomorphism \(\phi\), \(N \rtimes_\phi H\), and via the homomorphism
    \(\psi\), \(N \rtimes_\psi H\), are isomorphic if for \(\alpha \in \Aut{N}\) and \(\beta \in \Aut{H}\), we have:
    \[h^\beta\psi = \alpha^{-1}h\phi\alpha \tag{for all \(h \in H\)}\]
    That is, we can apply any automorphism to \(H\) and conjugate \(\Aut{N}\), and the resulting semidirect product remains in
    the same isomorphism class.
\end{lemma}

\begin{proof}
    Let \(G = N \rtimes_\phi H\) and \(\bar{G} = N \rtimes_\psi H\), and define:
    \[\theta:G \to \bar{G} \quad \text{by} \quad \theta:(n,\,h) \mapsto (n^\alpha,\,h^\beta)\]
    We will show that \(\theta\) is an isomorphism.

    First, \(\theta^{-1}\) exists because both \(\alpha^{-1}\) and \(\beta^{-1}\) exist.
    We can check that the inverse is given by:
    \[\theta^{-1}:(n,\,h) \mapsto (n^{\alpha^{-1}},\,h^{\beta^{-1}})\]
    Hence \(\theta\) is a bijection.
    We also have that:
    \[h^\beta\psi = \alpha^{-1}h\phi\alpha\]
    which implies:
    \[\alpha h^\beta\psi = h\phi\alpha \tag{\ast}\label{eqn:semidirect_homo}\]
    Now for two elements, \((n_1,\,h_1),\ (n_2,\,h_2) \in G\), consider:
    \begin{align*}
        (n_1,\, h_1)\theta\ (n_2,\, h_2)\theta &= (n_1^\alpha,\, h_1^\beta)(n_2^\alpha,\, h_2^\beta) \\
        &= (n_1^\alpha {(n_2^\alpha)}^{h_1^\beta\psi},\, h_1^\beta h_2^\beta) \\
        &= (n_1^\alpha {(n_2^{h_1\phi})}^\alpha,\, h_1^\beta h_2^\beta) \tag{by~\ref{eqn:semidirect_homo}} \\
        &= ({(n_1 {(n_2)}^{h_1\phi})}^\alpha,\, {(h_1 h_2)}^\beta) \\
        &= (n_1 {(n_2)}^{h_1\phi},\, h_1 h_2)\theta \\
        &= (n_1,\, h_1)(n_2,\, h_2)\theta
    \end{align*}
    So \(\theta\) is an isomorphism.
\end{proof}


% ====   Presentations   ====
\section{Presentations}
To encode groups succinctly, we will use \emph{group presentations}.
Their notation is like a combination of subgroup generators and set builder notation.
Presentations are formally defined in terms of subgroup of free groups, which is tangential to this report.
Moreover, presentations in general are a bit difficult to work with --- it turns out to be algorithmically impossible to
determine whether two group presentations are the same!
For our purposes, a loose definition will be enough.

\begin{definition}[Informal]
    In this report, a \emph{group presentation} has 3 main parts:
    \begin{enumerate}[(i)]
        \item A list of generators.
        \item How the generators themselves behave.
        \item How the generators interact.
    \end{enumerate}
\end{definition}

Let's illustrate this with a couple of examples.
First, let's look at a simple presentation, and understand how it works.
\[
    C_4 = \gen{x \mid x^4 = 1}
\]
We see that to the left of the mid-line, we have a generator \(x\), and to the right, \(x^4 = 1\) tells us that \(x\)
has order 4.
There is only a single generator, so there are no other generators to specify how they interact.

For the second example, let's build a presentation for \(D_8\).
We know that the dihedral group has 2 generators, a rotation \(r\), and a flip \(s\).
So we start writing:
\[
    \langle\, r,\,s
\]
The first generator, \(r\), has order 4, and \(s\) has order 2.
Let's record that:
\[
    \langle\, r,\,s \mid r^4 = s^2 = 1
\]
Finally, we know how the relate, namely \(s^{-1} rs = r^{-1}\).
So we finish the presentation:
\[
    D_8 = \gen{r,\,s \mid r^4 = s^2 = 1,\ s^{-1}rs = r^{-1}}
\]
Presentations will be especially useful for encoding semidirect products, because we can write the generators for the
subgroups in the product, specifying their order and how they interact, and then the effect of conjugation.

% ====   Group Actions   ====
\section{Group Actions}
Another useful piece of group theory technology will be group actions.
As above, much of this section is based on \textit{MT5864}, and can be found in Chapter 1 of Robinson.\footcite{robinson1982}

\begin{definition}
    \raggedright
    Let \(G\) be a group, and \(\Omega\) be a set, with elements \(g \in G\) and \(\omega \in \Omega\).
    Consider a map \(\mu:\Omega \times G \to \Omega\), and write \(\omega^g\) for the image of \((\omega,\,g)\) under
    \(\mu\).
    So we have:
    \[\mu:\Omega \times G \to \Omega \quad \text{defined by} \quad (\omega,\,g) \mapsto \omega^g\]
    We say \(G\) \emph{acts on} \(\Omega\) if for all \(g_1,\,g_2 \in G\) and all \(\omega \in \Omega\):
    \begin{enumerate}[(i)]
        \item \({(\omega^{g_1})}^{g_2} = \omega^{(g_1 g_2)}\)
        \item \(\omega^1 = \omega\)
    \end{enumerate}
    We call \(\mu\) the \emph{group action} of \(G\) on \(\Omega\).
\end{definition}

This might remind you of a homomorphism.
Indeed we have a result:

\begin{lemma}\label{lem:actionhom}
    \raggedright
    A group action induces a homomorphism.
    Specifically, let \(G\) be a group which acts on a set \(\Omega\), with \(g \in G\) and \(\omega \in \Omega\), and
    define:
    \[\rho_g:\Omega \to \Omega \quad \text{by} \quad \omega \mapsto \omega^g\]
    Then:
    \[\rho:G \to \Sym{\Omega} \quad \text{defined by} \quad g \mapsto \rho_g\]
    is a homomorphism.
\end{lemma}

\begin{proof}
    Firstly, \(\rho_g\) is indeed a permutation of \(\Omega\) because it is invertible (and therefore a bijection),
    with \({(\rho_g)}^{-1} = \rho_{g^{-1}}\).
    For \(\omega \in \Omega\):
    \[ \omega \rho_g \rho_{g^{-1}} = {(\omega^g)}^{g^{-1}} = \omega^{gg^{-1}} = \omega \]
    \[ \omega \rho_{g^{-1}} \rho_g = {(\omega^{g^{-1}})}^g = \omega^{g^{-1}g} = \omega \]
    Consider \(g,\,h \in G\) and their corresponding maps, \(\rho_{g},\,\rho_{h} \in \Sym{\Omega}\).
    Then:
    \[\omega(g\rho)(h\rho) = \omega\rho_g\rho_h = {(\omega^g)}^h = \omega^{(gh)} = \omega\rho_{gh} = \omega(gh)\rho\]
    Thus \(\rho\) is a homomorphism.
\end{proof}

By this we see that in a semidirect product, \(N \rtimes H\), the group \(H\) acts on \(N\)!

\begin{definition}
    \raggedright
    The \emph{orbit} of an element \(\omega \in \Omega\), is the set:
    \[\omega^G = \{\,\omega^x \mid x \in G\,\}\]
\end{definition}

A group acting on the set its cosets will be useful:

\begin{definition}
    \raggedright
    For a group \(G\) with \(H \leqslant G\), let \(\Omega = \{\,Hg \mid g \in G\,\}\), i.e.\ the set of cosets of \(H\)
    in \(G\).
    If \(x \in G\), define a group action:
    \[\mu:\Omega \times G \to \Omega \quad \text{by} \quad (Hg, x) \mapsto Hgx\]
\end{definition}

\begin{lemma}
    \raggedright
    A group's action on it's cosets is \emph{well defined}, meaning the action is independent of our choice of
    representative.
\end{lemma}

\begin{proof}
    We will show the lemma is true for right cosets.
    A similar argument shows the same for left cosets.

    Suppose \(G\) is a group with non-trivial subgroup \(H\), and let \(\Omega\) be the set of right cosets of \(H\).
    Let \(k,l \in G\) be representatives from the same coset, and we will show that \((Hk)\mu = (Hl)\mu\).
    Because \(k\) and \(l\) are in the same coset:
    \[ Hk = Hl \]
    And so \(H = H(lk^{-1})\) implies that \(lk^{-1} \in H\).
    Then:
    \[ (Hl)\mu = H(lx) = H(lk^{-1}kx) = H(kx) = (Hk)\mu \]
    Hence \(\mu\) is well defined.
\end{proof}

