% ====   Order 12   ====
\section{Groups of order 12}
We will see later, that we need groups of order 12 as a special case for groups of order \(p^2q\) for prime numbers
\(p\) and \(q\).

Let \(G\) be a group of order \(12 = 2^2 \cdot 3\), and \(n_3\) and \(n_2\) denote the number of Sylow 3-subgroups and
Sylow 2-subgroups of G respectively.
By Theorem~\ref{thm:sylow3}:
\[n_2 \equiv 1 \text{ (mod 2) and } n_2 \mid 3 \implies n_2 = 1\]
\[n_3 \equiv 1 \text{ (mod 3) and } n_3 \mid 4 \implies n_3 = 1 \ \text{or} \ 4\]

So \(G\) has a unique Sylow 2-subgroup of order 4, say \(H \nrmsgp G\), and we have already classified groups of order 4,
so \(H\) is isomorphic to either \(V_4\) (the Klein 4 group) or \(C_4\).
A Sylow 3-subgroup, \(K \leqslant G\) will have order 3, so \(K \cong C_3\).
Say \(K = \langle x \rangle\).

Lagrange's Theorem tells us \(H\) has elements of order 1, 2, and 4, and \(K\) has elements of order 1 and 3.
Hence \(H \cap K = \bm{1}\).
Lemma~\ref{lem:setprodorder} tells us:
\[|HK| = |H| \cdot |K| = 12\]
Hence \(G = HK\), \(H \nrmsgp G\), and \(H \cap K = \bm{1}\).
If we consider groups with 4 Sylow 3-subgroups then we can conclude that they are some semidirect product, \(G = H
\rtimes K\).

Since an automorphism, \(\varphi\), must map generators to generators, \(\Aut{C_4} \cong C_2\) because \(C_4\) has two
generators.
An automorphism of \(V_4\) corresponds to a permutation of the three
non-identity elements, hence \(\Aut{V_4} \cong S_3\).

\begin{enumerate}[\bfseries{Case} 1:]
    \item \(H \cong C_4\) i.e. \(G \cong C_4 \rtimes C_3\).

        Let \(H = \langle y \rangle\).

        A homomorphism \(\psi:K \to \Aut{H} \cong C_2\), preserves order and together with Lagrange's Theorem means that
        the only possibility for \(\psi\) is trivial, i.e. \(K\psi = \bm{1}\).

        Hence \(G \cong C_4 \times C_3 \cong C_{12}\).

    \item \(H \cong V_4\) i.e. \(G \cong (C_2 \times C_2) \rtimes C_3\).

        Let \(H = \langle y, z \rangle\).

        A trivial homomorphism \(K\psi = \bm{1}\) yields the direct product.
        What non-trivial homomorphisms are there?
        The automorphism group, \(\Aut{H} \cong S_3\) is of order 6, and so has a unique subgroup of order 3, by
        Theorem~\ref{thm:sylow3}.
        We know already that a homomorphism \(\psi: K \to \Aut{H}\) is determined by where it sends the generator
        \(x\), so for \(\psi\) to be non-trivial, it must send \(x\) to an element of order 3 in \(\Aut{H}\).

        There are 2 such elements.
        Because \(\Aut{H} \cong S_3\), we will think of them as the permutations of order 3 of the set \(\{1, 2, 3\}\).
        Denote them \(a = (1\ 2\ 3)\) and \(b = (1\ 3\ 2)\).
        Notice that \(b = a^{-1}\), so we have homomorphisms:
        \[\psi_1:x \mapsto a \quad \text{and} \quad \psi_2:x \mapsto a^{-1}\]
        It appears we have 2 choices, but this is not the case.
        If we define \(\theta:K \to K\) by \(x\theta = x^{-1}\) then \(\theta\psi_1 = \psi_2\).
        And notice that \(\theta\) is an automorphism of \(K\), so the semidirect products with \(\psi_1\) and \(\psi_2\)
        are isomorphic.
        Hence (up to isomorphism) there is one non-trivial homomorphism \(\psi:K \to \Aut{H}\).
        So \(x \in K\) acts by permuting the 3 non-identity elements of \(H\).

        We will show that in this case, \(G \cong A_4\).
        First, let's check \(A_4\) has the same subgroup structure as \(G\).
        There is a subgroup isomorphic to \(C_3\) in \(A_4\), generated by the 3-cycle \((1\ 2\ 3)\):
        \[\bar{K} = \langle (1\ 2\ 3) \rangle\]
        We can also find a subgroup isomorphic to \(V_4\):
        \[\bar{H} = \{\,1,\, (1\ 2)(3\ 4),\, (1\ 3)(2\ 4),\, (1\ 4)(2\ 3)\,\}\]
        Indeed, we can check that \(\bar{H}\) is normal in \(A_4\).
        We can see that \(\bar{H} \cap \bar{K} = \bm{1}\) because \(\bar{H}\) contains no 3-cycles, and that
        \(\bar{H}\bar{K} = A_4\).
        So we can conclude that \(A_4 = \bar{H} \rtimes \bar{K}\).

        Let's investigate haw
        If we let \(\alpha = (1\ 2)(3\ 4)\), \(\beta = (1\ 4)(2\ 3)\) and \(\gamma = (1\ 2\ 3)\), then we can write an
        element of \(A_4\) as \(\alpha^i\beta^j\gamma^k\) for some \(i\), \(j\) and \(k\).
        Define \(\phi:A_4 \to G\) by \(\phi:\alpha^i\beta^j\gamma^k \mapsto x^{i}y^{j}z^{k}\).
        Then:
        \[\beta\phi = (\gamma^{-1}\alpha\gamma)\phi = c^{-1}ac = b\]
        So conjugation acts in the same way.
        Hence we can conclude that \(G \cong A_4\).
\end{enumerate}

If we instead consider \(G\) where \(K \nrmsgp G\), i.e. \(G = K \rtimes H\), then we again have two cases:

\begin{enumerate}[\bfseries{Case} 1:]
    \item \(H \cong C_4\) i.e. \(G \cong C_3 \rtimes C_4\).

        Let \(H = \langle y \rangle\).

        We know \(\Aut{C_3} \cong C_2\) so a homomorphism \(\psi\) maps \(H\) to the trivial group or to \(\langle
        \beta:x \mapsto x^{-1} \rangle\).

        If \(H\psi = \bm{1}\) then \(G = K \times H \cong C_4 \times C_3\), which we have already seen.

        If \(H\psi = \langle \beta \rangle\) then we have:
        \[G = \langle\, x, y \mid x^3 = y^4 = 1,\ y^{-1}xy = x^{-1}\,\rangle\]
        Now let \(a = xy^2\).
        And remember, \(y^{-1}xy = x^{-1}\) means \(x\) commutes with \(y^2\).
        So now:
        \[a^3 = xy^2xy^2xy^2 = x^3y^6 = y^2\]
        and
        \[b^{-1}ab = y^{-1}xy^2y = (y^{-1}xy)y^2 = x^{-1}y^2 = y^2x^{-1} = a^{-1}\]
        So:
        \[G = \langle\, a,\,b \mid a^6 = 1,\ a^3 = b^2,\ b^{-1}ab = a{-1}\,\rangle\]
        This is known as the \emph{binary dihedral} or \emph{dicyclic} group, denoted \(\Dic_{12}\).

    \item \(H \cong V_4\) i.e. \(G \cong C_3 \rtimes (C_2 \times C_2)\).

        Let \(H = \langle y, z \rangle\).

        If \(\psi:H \to \Aut{K}\) is trivial then we obtain the direct product again.

        The image of a non-trivial homomorphism \(\psi:H \to \Aut{K}\) is isomorphic to \(C_2\), so by
        Theorem~\ref{thm:iso1}: \(\ker{\psi} \cong C_2\).

        We can choose \(\psi\) such that \(y\psi = \beta:x \mapsto x^{-1}\) and \(z\psi = \iota:x \mapsto x\).
        Then:
        \[G = \langle\, x, y, z \mid x^3 = y^2 = z^2 = 1,\ yz = zy,\ y^{-1}xy = x^{-1},\ z^{-1}xz = x\,\rangle\]
        Let \(a = xz\).
        The order of \(a = \lcm{(\order{(x)}, \order{(z)})} = \lcm{(2, 3)} = 6\) because \(x\) and \(z\) commute.
        So:
        \[a^3 = x^3z^3 = z\]
        and
        \[ y^{-1}ay = y^{-1}xzy = y^{-1}xyz = x^{-1}z = x^2z = a^2a^3 = a^{-1}\]
        Hence:
        \[G = \langle\, y, a \mid a^6 = y^2 = 1,\ a^{-1}ay = a^{-1}\,\rangle
        \cong D_{12}\]
\end{enumerate}

So a group \(G\) of order 12 is isomorphic to one of:
\[
    C_{12}, \quad%
    C_2 \times C_6, \quad%
    A_4, \quad%
    D_{12}, \quad \text{or} \quad%
    \Dic_{12}
\]

