% ====   Preliminaries   ====
\section{Preliminaries}
To start, let's solidify the notation used in this report.

We shall denote groups and sets with capital letters, like \(G\), \(H\), and elements of those groups with lower case
letters, like \(g\), \(h\).
Greek letters shall denote mappings, generally \(\phi\), \(\psi\), etc.\ with \(\iota\) reserved for the identity map,
and we will write mappings on the right.

We will use \(\N\) to denote the natural numbers (not including 0), \(\Z\) to denote the integers, and \(\R\) to denote
the real numbers.

To denote the cyclic group of order \(n\) we will use \(C_n\), \(D_{2n}\) to denote the cyclic group of order \(2n\),
\(A_n\) to denote the alternating group over \(n\) elements, \(S_n\) to denote the symmetric group over \(n\)
elements, and \(Q_8\) to denote the quaternion group.
The trivial group, \(\{\, 1\, \}\) is denoted by \(\bm{1}\).

Let's move on to review some facts and theorems which will be valuable later on, as well as introduce some new concepts
and prove some new results!

\begin{definition}
    A \emph{permutation} of a set \(X\) is a bijection from \(X\) to \(X\).
    The \emph{symmetric group} \(X\) is the set of all permutations of \(X\) under composition.
    We write \(\Sym{X}\) to denote this.
    It is easy to show \(\Sym{X}\) is a group.
\end{definition}



\begin{definition}
    If \(G\) is a group, and \(H \subseteq G\), then \(H\) is a \emph{subgroup} of \(G\) if it is a group in its own right with
    the multiplication from \(G\).
    We write \(H \leqslant G\) to mean \(H\) is a subgroup of \(G\).

    If \(H\) is closed under \emph{conjugation}, i.e.\ for all \(g \in G\) and \(h \in H\), \(g^{-1}hg \in H\), then we
    say \(H\) is a \emph{normal subgroup} of \(G\).
    We write \(H \nrmsgp G\) to mean \(H\) is a normal subgroup of \(G\).
\end{definition}

\begin{definition}
    If \(G\) is a group and \(X \subseteq G\), then the \emph{subgroup generated by \(X\)} is the intersection of all
    subgroups of \(G\) containing \(X\).
    This in denoted \(\langle X \rangle\).
    The proof that \(\langle X \rangle\) is a subgroup of \(G\) is omitted.
    The elements of \(X\) are called \emph{generators} of \(G\).
\end{definition}

\begin{definition}
    If \(G\) is a group with subgroup \(H\) then the \emph{right coset} of \(H\) in \(G\) with representative \(g \in
    G\) is:
    \[Hg = \{\,hg \mid h \in H\,\}\]
\end{definition}


\begin{definition}
    The \emph{order} of a group, \(G\), is the number of elements in \(G\), denoted \(|G|\).
    The \emph{order} of an element \(g \in G\) is the smallest \(i \in \N\) such that \(g^i = 1\).
\end{definition}

\begin{definition}
    If \(G\) and \(H\) are groups with elements \(g_1,\, g_2 \in G\), then a map:
    \[\phi:G \to H\]
    is a \emph{homomorphism} if:
    \[(g_1 g_2)\phi = (g_1\phi)(g_2\phi)\]
    If \(\phi\) is bijective, then we call it an \emph{isomorphism}, with \(G \cong H\) denoting that \(G\) is
    isomorphic to \(H\).
    And if \(\phi\) is an isomorphism from \(G\) to itself, then we call it an \emph{automorphism} of \(G\).
\end{definition}

\begin{lemma}
    The set of all automorphisms of a group \(G\) form a group under composition.
    Indeed, this is called the \emph{automorphism group} of \(G\), denoted \(\Aut{G}\).
\end{lemma}

\begin{proof}
    Let \(A = \Aut{G} = \{\,\phi:G \to G \mid \phi\ \text{is an isomorphism}\,\}\), and let \(\phi \in A\).
    Denote an element of \(G\) by \(g\).

    We know already that the composition of two isomorphisms is an isomorphism, so \(A\) is closed under composition.

    The identity map, \(\iota:g \mapsto g\), is certainly an automorphism of \(G\) and so \(A \neq \varnothing\).

    Indeed, \(\iota:g \mapsto g\) is the identity of \(A\), since:
    \[g\phi\iota = (g\phi)\iota = g\phi \quad \text{and} \quad g\iota\phi = (g\iota)\phi = g\phi\]

    And inverses clearly exists, because automorphisms are bijections, and bijections are invertible.
    Hence \(A = \Aut{G}\) is a group.
\end{proof}

\begin{lemma}\label{lem:aut}
    The automorphism group of \(C_n\) is isomorphic to the multiplicative group
    of integers mod \(n\).

    i.e. \(\Aut{C_n} \cong \units{n}\)
\end{lemma}

\begin{proof}
    Let \(C_n = \langle x \rangle\).
    Any automorphism, \(\varphi\) of \(C_n\) has the property:
    \[(x^i)\varphi = {(x\varphi)}^i\]
    Hence \(\varphi\) is determined by it's effect on a generator, \(x\), and preserves element
    order.
    In particular, \(\varphi\) sends generators to generators.
    So for \(\varphi\) to be an automorphism, it must send \(x\) to another generator, say \(x^k\).
    An element \(x^k\) generates \(C_n\) if \(x^k\) has order \(n\), i.e.\ when \(k\) and \(n\) are co-prime.
    Denote the automorphism sending \(x\) to \(x^k\) by \(\varphi_k\).

    Let's now investigate how these automorphisms behave.
    Let \(\varphi_k, \varphi_l \in \Aut{C_n}\), and consider:
    \[x\varphi_k\varphi_l = (x^k)\varphi_l = {(x^k)}^l = x^{(kl)} = x\varphi_{kl} \quad \text{(mod \(n\))}\]
    Because multiplication modulo \(n\) is commutative, \(x^{kl} = x^{lk}\), so \(\Aut{C_n}\) is abelian.

    Now consider \(\theta:\Aut{C_n} \to \units{n}\) defined by \(\varphi_k\theta = k\).
    We will show \(\theta\) is an isomorphism.
    Every \(k \in \units{n}\) is co-prime to \(n\) and so \(x^k\) is a generator of \(C_n\), hence there is some \(\varphi_k
    \in \Aut{C_n}\) such that \(\varphi_k\theta = k\).
    So \(\theta\) is surjective.
    If \(\varphi_k\theta = \varphi_l\theta\) then \(k = l\), so \(\theta\) is also injective.
    Finally, \(\theta\) is a homomorphism because:
    \[(\varphi_k\varphi_l)\theta = \varphi_{kl}\theta = kl = (\varphi_k\theta)(\varphi_l\theta)\]
    So \(\theta:\Aut{C_n} \to \units{n}\) is an isomorphism.
\end{proof}

\begin{theorem}[Lagrange's Theorem]

\end{theorem}

\subsection{Sylow Theorems}
This collection of theorems is extremely useful for describing subgroup structure.
Hopefully these ring some bells.
Let \(G\) be a group of order \(p^n m\) where \(p\) is a prime and \(p\nmid m\).
\begin{theorem}[\nth{1} Sylow Theorem]\label{thm:sylow1}
    \(G\) has a Sylow \(p\)-subgroup, i.e.\ a subgroup of order \(p^n\).
\end{theorem}
\begin{theorem}[\nth{2} Sylow Theorem]\label{thm:sylow2}
    All Sylow \(p\)-subgroups of \(G\) are conjugate to each other.
    In particular, if \(G\) has a unique Sylow \(p\)-subgroup, then it is a normal subgroup.
\end{theorem}
\begin{theorem}[\nth{3} Sylow Theorem]\label{thm:sylow3}
    Let \(n_p\) denote the number of Sylow \(p\)-subgroups of \(G\).
    Then:
    \begin{enumerate}[(i)]
        \item \(n_p \mid m\)
        \item \(n_p\equiv 1\) (mod \(p\))
    \end{enumerate}
\end{theorem}

% TODO: Write out isom theorems
\subsection{Isomorphism Theorems}
\begin{theorem}\label{thm:iso1}
\end{theorem}

\begin{theorem}\label{thm:iso2}
\end{theorem}

\begin{theorem}\label{thm:iso3}
\end{theorem}

\subsection{Semidirect Product}
We already know about the direct product:

\begin{definition}[Direct Product]
    For groups \(N\) and \(H\), the \emph{direct product}, \(G = N\times H\) is a group of ordered pairs of elements
    \((n, h)\) where \(n \in N\) and \(h \in H\) with the operation:
    \[(n_1, h_1)(n_2, h_2) = (n_1n_2, h_1h_2)\]

    Moreover, if \(\bar{N} = N \times \bm{1}\) and \(\bar{H} = \bm{1} \times H\), then:
    \begin{enumerate}[(i)]
        \item \(\bar{N} \nrmsgp G\) and \(\bar{H} \nrmsgp G\)
        \item \(\bar{N} \cap \bar{H} = \bm{1}\)
        \item \(\bar{N}\bar{H} = \{\,nh \mid n \in N,\ h \in H\,\} = G\)
    \end{enumerate}
\end{definition}

Now let's seek a slightly more general way to combine groups, by relaxing that \(H\) must be normal.
So we have:
\[N \nrmsgp G,\ H \leqslant G,\ NH = G, \quad \text{and} \quad N \cap H = \bm{1}\]
Consider the \emph{set}, (not the direct product):
\[N \times H = \{\,(n,\,h) \mid n \in N,\ h \in H\,\}\]
and a map
\[\phi:N \times H \to G \quad \text{defined by} \quad (n,\, h) \mapsto nh\]
We want \(\phi\) to be an isomorphism.

To show \(\phi\) is injective, take \(n_1,\, n_2 \in N\) and \(h_1,\, h_2 \in H\), and assume \(n_1 h_1 = n_2 h_2\).
Then multiplying on the left by \(n_2^{-1}\) and on the right by \(h_1^{-1}\) gives:
\[n_2^{-1} n_1 = h_2 h_1^{-1}\]
On the left we have an element of \(N\) and on the right, an element of \(H\), so \(n_2^{-1} n_1 = h_2 h_1^{-1} \in N
\cap H\).
But \(N \cap H = \bm{1}\) so then \(n_2^{-1} n_1 = h_2 h_1^{-1} = 1\).
Hence:
\[n_1 = n_2 \quad \text{and} \quad h_1 = h_2\]

To show \(\phi\) is surjective, consider the image, \(\im{\phi} = \{\,nh \mid n \in N,\ h \in H\,\}\).
This is by definition \(NH = G\), so \(\phi\) is surjective, and hence a bijection.

For \(\phi\) to be a homomorphism, we need:
\begin{equation*}
\begin{aligned}
    \relax[(n_1,\,h_1)(n_2,\,h_2)]\phi &= (n_1,\,h_1)\phi\,(n_2,\,h_2)\phi \\
    &= n_1 h_1 n_2 h_2 \\
    &= n_1 h_1 n_2 h_1^{-1} h_1 h_2 \\
    &= (n_1 h_1 n_2 h_1^{-1})(h_1 h_2)
\end{aligned}
\end{equation*}
But \(N\) is normal in \(G\) so \(h_1 n_2 h_1^{-1}\) is just another element in \(N\), say \(n_3\).
So:
\[\relax[(n_1,\,h_1)(n_2,\,h_2)]\phi = (n_1 n_3)(h_1 h_2) = (n_1 n_3,\,h_1 h_2)\phi\]
We know that \(\phi\) is injective, so then:
\[(n_1,\,h_1)(n_2,\,h_2) = (n_1 n_3,\,h_1 h_2)\]
This tells us the multiplication that will make \(NH\) a group.
Because \(N \nrmsgp G\), the map
\[\varphi_{h_1}:n_2 \mapsto h_1 n_2 h_1^{-1} = n_3\]
is an automorphism of \(N\).
This gives rise to the definition:

\begin{definition}[Semidirect Product]
\mbox{}
\begin{enumerate}[(i)]
    \item

        For a group \(G\) with normal subgroup \(N\) and subgroup \(H\) with \(NH = G\) and \(N \cap H = \bm{1}\),
        \(G\) is the \emph{internal semidirect product} of \(N\) by \(H\), written \(G = N \rtimes H\).

    \item

        For groups \(N\) and \(H\), and a homomorphism \(\psi:H \to \Aut{N}\), the \emph{external semidirect product} of
        \(N\) by \(H\) via \(\psi\) is the set:
        \[N \times H = \{\,(n,\,h) \mid n \in N,\ h \in H\,\}\]
        with multiplication:
        \[(n_1,\,h_1)(n_2,\,h_2) = (n_1(n_2\phi_{h_1}),\,h_1 h_2)\]
        denoted:
        \[N \rtimes_{\psi} H\]

\end{enumerate}
\end{definition}

\begin{lemma}\label{lem:setprodorder}
    For a group \(G\) with \(N \leqslant G\) and \(H \leqslant G\), with \(N \cap H = \bm{1}\) then:
    \[|NH| = |\{nh \mid n \in N, h \in H\}| = |N| \cdot |H|\]
\end{lemma}

\begin{proof}
    We just saw above that for elements \(n \in N\) and \(h \in H\), the map:
    \[\phi:N \times H \to NH \quad \text{defined by} \quad (n,\,h) \mapsto nh\]
    is a bijection.
    The result follows immediately from this.
\end{proof}

\subsection{Group Actions}
Some snazzy introduction.

\begin{definition}
    Let \(G\) be a group, and \(\Omega\) be a set, with elements \(g \in G\) and \(\omega \in \Omega\).
    Consider a map \(\mu:\Omega \times G \to \Omega\), and write \(\omega^g\) for the image of \((\omega,\,g)\) under
    \(\mu\).
    So we have:
    \[\mu:\Omega \times G \to \Omega \quad \text{defined by} \quad (\omega,\,g) \mapsto \omega^g\]
    We say \(G\) \emph{acts on} \(\Omega\) if for all \(g_1,\,g_2 \in G\) and all \(\omega \in \Omega\):
    \begin{enumerate}[(i)]
        \item \({(\omega^{g_1})}^{g_2} = \omega^{(g_1 g_2)}\)
        \item \(\omega^1 = \omega\)
    \end{enumerate}
    We call \(\mu\) the \emph{group action} of \(G\) on \(\Omega\).
\end{definition}

This might remind you of a homomorphism.
Indeed we have a result:

\begin{lemma}\label{lem:actionhom}
    A group action induces a homomorphism.
    Specifically, let \(G\) be a group which acts on a set \(\Omega\), with \(g \in G\) and \(\omega \in \Omega\), and
    define:
    \[\rho_g:\Omega \to \Omega \quad \text{by} \quad \omega \mapsto \omega^g\]
    Then:
    \[\rho:G \to \Sym{\Omega} \quad \text{defined by} \quad g \mapsto \rho_g\]
    is a homomorphism.
\end{lemma}

\begin{proof}
    Firstly, \(\rho_g\) is indeed a permutation of \(\Omega\) because it is invertible (and therefore a bijection),
    with:
    \[{(\rho_g)}^{-1} = \rho_{g^{-1}}\]
    Consider \(g,\,h \in G\) and their corresponding maps, \(\rho_{g},\,\rho_{h} \in \Sym{\Omega}\).
    Then:
    \[\omega(g\rho)(h\rho) = \omega\rho_g\rho_h = {(\omega^g)}^h = \omega^{(gh)} = \omega\rho_{gh} = \omega(gh)\rho\]
    Thus \(\rho\) is a homomorphism.
\end{proof}

A group acting on the set its cosets will be very useful:

\begin{definition}
    For a group \(G\) with \(H \leqslant G\), let \(\Omega = \{\,Hg \mid g \in G\,\}\), i.e.\ the set of cosets of \(H\)
    in \(G\).
    If \(x \in G\), define a group action:
    \[\Omega \times G \to \Omega \quad \text{by} \quad (Hg, x) \mapsto Hgx\]
\end{definition}

\begin{lemma}
    The action above is \emph{well defined}, meaning the action is independent of our choice of representative \(g\).
\end{lemma}

\begin{proof}
    % TODO
\end{proof}
